\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-02-16 forwards-and-backwards.tex
mmt first draft

\comment{We talked about having the next paragraph be a Proposition or something?
I am putting off rewriting this paragraph until I know what has been proved.}

@@

\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
    As in Section~\ref{sec:population_density_proof},
    the theorem will follow from tightness and characterization of the limit.
    This time, the processes $\lp^N$ take values in $\lpmeasures$,
    the space of locally finite measures on space $\times$ levels.
    (They will in fact be point measures, including the limit,
    but that is a consequence of this theorem.)

    Again, tightness follows from a compact containment condition,
    tightness of one-dimensional distributions,
    and an application of \citet{EK} Theorem~3.9.1.

    % Lines of descent can escape to infinite level in finite time, and so
    % we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
    \comment{Should this be a separate definition (along the lines of Condition 2.1 in \citet{etheridge/kurtz:2018})?}
    Let $\{h_k\}$ be a separating class of nonnegative functions in $C^1_b([0, \infty))$
    such that
    $\int_0^\infty \int_u^\infty h_k(v) dv du$,
    $\int_0^\infty u^2 |h_k'(u)| du$,
    and $\int_0^\infty h_k(u)^2 du$
    are all finite for all $k$,
    and assume furthermore that $h_0$ is a positive, nonincreasing function 
    that bounds all other $h_k$, i.e., for any $k$,
    there is a $c_k$ such that $h_k(u) \le c_k h_0(u)$ for all $u \ge 0$.
    (For instance, we may take $h_0(u) = e^{-u}$ and the remaining $h_k$
    to be a separating class of $C^1$ functions with compact support.)
    Following \citet{etheridge/kurtz:2018} (see Condition 2.1),
    we endow $\lpmeasures$ with
    the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
    of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
    and $h \in \{h_k\}_{k \ge 0}$.
    This space is completely metrizable,
    and a subset $K \subset \lpmeasures$ is relatively compact if and only if
    $\sup_{\lp \in K} \langle h_k, \lp \rangle < \infty$ for each $k$;
    therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.

@@

@@

In other words, the processes $\lp^N$ stay in 
the compact set
$$
    \left\{
        \lp \in \lpmeasures \;:\;
        \langle h_k, \lp \rangle \le C_k
        \text{ for all } k \ge 1
    \right\} ,
$$
for all $0 \le t \le T$
with uniformly high probability.
We will prove this Lemma using the following one:

\begin{lemma}
    \label{lem:compact containment hn}
    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$ and $k$ there exists a constant $K_k$ such that
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
    <
    \frac{K_k}{M} .
    $$
\end{lemma}

@@

\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
    \comment{TODO: shorten and make constants have reasonable notation}
    First note that since $h_k(u) \le c_k h_0(u)$ for all $u$,
    so $\langle h_k, \lp_t^N \rangle \le c_k \langle h_0, \lp_t^N \rangle$,
    and so we need only prove the Lemma for $h_0$.
    Henceforth, let $h = h_0$.
    Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
    \begin{align*}
    \begin{split}
        \langle h, \lp_t^N \rangle
        &=
        \langle h, \lp_0^N \rangle
        + M^{h}_t 
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 c^N(x, \eta^N_s) \int_u^N h(v) dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \\ & \qquad \qquad {}
        +
        \int_0^t
        \big\langle
            \left(
                c^N(x, \eta^N_s) u^2
                - b^N(x, \eta^N_s) u
            \right)
            h'(u)
        ,
        \lp_s^N(dx, du) \big \rangle
        ds ,
    \end{split}
    \end{align*}
    where $M^{h}_t$ is a martingale
    with quadratic variation
    \begin{align*}
        [M^{h}]_t
        &=
        \int_0^t
        \langle 2 c^N(x, \eta_s^N) \int_u^N h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{align*}
    Now, note that $0 \le c^N(x, \eta_x^N) \le C_a < \infty$
    and $b^N(x, \eta_s^N) \le C_b < \infty$,
    and we have assumed that $h'(u) \le 0$ (since $h_0$ is nonincreasing),
    so we may bound
    \begin{align} \label{eqn:hn_bound},
    \begin{split} 
        \langle h, \lp_t^N \rangle
        &\le
        \langle h, \lp_0^N \rangle
        + M^{h}_t
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 C_a \int_u^\infty h(v) dv
            + \left( C_a u^2 + C_b u \right) |h'(u)|
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{split}
    \end{align}
    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
    we know that for appropriate $f$,
    $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
    where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
    By our assumptions on $h=h_0$,
    we know that
    $$
        \int_0^\infty \left( 2 C_a \int_u^\infty h(v) dv
        + \left( C_a u^2 + C_b u \right) |h'(u)| \right) du
        < C
    $$
    for some $C < \infty$, and so
    \begin{align*}
    \begin{split}
        \IE\left[ \langle h, \lp_t^N \rangle \right]
        &\le
        \IE\left[ \langle h, \lp_0^N \rangle \right]
        +
        C
        \int_0^t
        \IE\bigg[
            \big\langle
            1
            ,
            \eta_s^N(dx, du) \big \rangle
        \bigg]
        ds ,
    \end{split}
    \end{align*}
    which we know by Lemma~\ref{lem:eta_f_bound}
    is bounded by $C_0 e^{C_1 t}$ for some other constants $C_0$ and $C_1$.

@@

    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
    The Burkholder-Davis-Gundy inequality
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c^N(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & =
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C'' e^{C_1 T} ,
    \end{align*}
    for a constant $C''$ which is finite
    by our assumption that $\int_0^\infty h_0(v)^2 dv < \infty$.

@@

\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
    Again, we use the Aldous-Rebolledo criterion.
    Tightness of $\langle f, \lp_t \rangle$ for a fixed $t$
    follows from Lemma~\ref{lem:compact containment hn},
    so we need only prove conditions analogous to
    \eqref{eqn:eta_projections_goal1}
    and \eqref{eqn:eta_projections_goal2}
    applied to the martingale representation
    of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
    Indeed, the proof follows exactly as the proof of
    Lemma~\ref{lem:eta_projections_tightness},
    except that terms are bounded by constant multiples of $\langle h_0, \xi^N_s \rangle$
    instead of $\langle 1, \eta^N_s \rangle$.
    There is only one term that might use explanation,
    which is
    \begin{align*}
        &
        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
        \\ &\qquad
        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
    \end{align*}
    but this is now bounded as in the proof of Lemma~\ref{lem:eta_f_bound}.
\end{proof}

@@

\subsection{Generator of Lookdown Representations}

We now define the generator of the lookdown representations.
\begin{definition}[Martingale Problem Characterisation]
    \label{defn:lookdown_mgale}
For given positive values of $N$ and $\theta$
and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
we define $(\lp^{N}_t)_{t \geq 0}$
to be the unique solution to the martingale problem
with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
\begin{equation*}
\begin{split}
& A^{N}f(\lp ) \\
&\quad =
    f(\lp)
    \,\sum_{(x,u)\in \lp}\,
    2 \gamma(x, \eta)
    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
            \frac{
                \theta \int_{\IR^d}
                (g(y,u) - g(x,u))
                r(y, \eta) q_{\theta}(x,dy)
            }{ g(x,u) }
        \\
    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
        \frac{\theta}{N} \int_u^N
        \int_{\IR^d}\left(
            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
        \right)
        r(y, \eta) q_{\theta}(x,dy)
        du_1
    \Bigg\}\\
    &\qquad\qquad {} +
    f(\lp) \sum_{(x,u)\in\lp}\,
    \left(
        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
    \right)
    \frac{\partial_u g(x,u)}{g(x,u)}
    ,
\end{split}
\end{equation*}
for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
as before.
\end{definition}

Similarly, 
we define the generator for the lookdown representation of the limiting spatial model.

\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
    \label{defn:limiting_lookdown_mgale}
    For a given value of $\alpha \in [0, \infty)$,
    define the operator $A$ acting on test functions of the form
    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
    Then, let $A f$ be
    \begin{equation}
    \begin{aligned} \label{eqn:limiting_lookdown_generator}
    A f(\lp)
    =&
        f(\lp)  \sum_{(x, u) \in \xi}
        \gamma(x, \eta)
            \frac{
                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
            }{
                g(x, u)
            }
    \\ &+
        f(\lp) \sum_{(x, u) \in \xi}
        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
    \\ &+
        f(\lp) \sum_{(x, u) \in \xi}
        \left(
            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
            -
            \left\{
                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
            \right\} u
        \right)
        \frac{\partial_u g(x, u)}{ g(x,u) }  .
    \end{aligned}
    \end{equation}

    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
    is a solution to the $(A, \lp_0)$ martingale problem
    if it has initial distribution $\lp_0$
    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
    as defined above.
\end{definition}

>>>>

Elsewhere we have written $\eta^N$ for the spatial projection of the lookdown process $\lp^N$,
although $\eta^N$ was defined first as a solution to a martingale problem.
For the purposes of this result --
the application of the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018} --
we must disambiguate these, and so define the spatial projection
maps $\gamma^N: \mathcal{M}(\IR^d \times [0, N]) \to \mathcal{M}(\IR^d)$
by $\gamma^N(\xi^N)(\cdot) = \xi^N(\cdot \times [0, N]) / N$,
and $\gamma: \mathcal{M}(\IR^d \times [0, \infty)) \to \mathcal{M}(\IR^d)$
by $\gamma(\xi)(\cdot) = \lim_{u_0 \to \infty} \xi(\cdot \times [0, u_0]) / u_0$.
We will also need an inverse notion:
for a measure $\lp^N$ on $\IR^d \times [0, N]$ and a sigma-field $\mathcal{F}$,
we say that \emph{$\lp$ is conditionally uniform given $\mathcal{F}$}
if for all compactly supported $f$,
\begin{align} \label{eqn:conditionally_uniform}
    \IE[ e^{-\langle f, \lp \rangle} \;|\; \mathcal{F} ]
    &=
    e^{-\langle F_f^N, \gamma(\lp) \rangle} ,
\end{align}
where
$$ F_f^N(x) = - N \log \frac{1}{N} \int_0^N e^{-f(x, u)} du . $$
(In other words, the $[0, N]$ components of $\lp$
are independent, uniformly distributed on $[0, N]$, and independent of $\gamma(\lp)$.)
Similarly, for a measure $\lp$ on $\IR^d \times [0, \infty)$
we say that \emph{$\lp$ is a conditionally Poisson random measure given $\mathcal{F}$}
if for all compactly supported $f$,
\begin{align} \label{eqn:conditionally_poisson}
    \IE[ e^{-\langle f, \lp \rangle} \;|\; \mathcal{F} ]
    &=
    e^{-\langle \int_0^\infty (1 - e^{-f(x, u)}) du, \gamma(\lp)(dx) \rangle} .
\end{align}
(In other words, $\lp$ is conditionally Poisson with Cox measure $\gamma(\lp) \times \Lambda$.)

\begin{proposition}
    \label{thm:mmt_application}
    Let $\mu_0$ be a probability distribution on $\measures$,
    and $\nu_0^N$ a probability distribution on $\mathcal{M}(\IR^d \times [0, N])$
    such that a draw $\lp^N_0$ from $\nu_0^N$ is conditionally uniform given $\gamma(\lp^N_0)$
    in the sense of \eqref{eqn:conditionally_uniform}.
    If $\tilde \eta^N$ is a solution
    of the martingale problem of Definition~\ref{defn:mgale_construction}
    with initial distribution $\mu_0$
    then there exists a solution $\lp^N$
    of the martingale problem of Definition~\ref{defn:lookdown_mgale}
    with initial distribution $\nu_0^N$
    such that $\eta^N = \gamma \cdot \lp^N$
    has the same distribution on $D_{\measures}[0, \infty)$
    as $\tilde \eta^N$.
    Furthermore, $\lp^N$ is conditionally uniform given given $\mathcal{F}^{\eta}_t$
    in the sense of \eqref{eqn:conditionally_uniform}.

    \comment{Theorem~\label{thm:nonlocal_convergence}
        isn't written as ``the $(A, \mu)$ martingale problem is'';
        rephrase here or there?}

    Similarly,
    let $\mu_0$ be a probability distribution on $\measures$,
    and $\nu_0$ a probability distribution on $\mathcal{M}(\IR^d \times [0, \infty))$
    such that a draw $\lp_0$ from $\nu_0$ is conditionally Poisson given $\gamma(\lp_0)$
    in the sense of \eqref{eqn:conditionally_poisson}.
    If $\tilde \eta$ is a solution
    of the limiting martingale problem of Theorem~\label{thm:nonlocal_convergence}
    with initial distribution $\mu_0$
    then there exists a solution $\lp$
    of the martingale problem of of Definition~\ref{defn:limiting_lookdown_mgale}
    with initial distribution $\nu_0$
    such that $\eta = \gamma \cdot \lp$
    has the same distribution on $D_{\measures}[0, \infty)$
    as $\tilde \eta$.
    Furthermore, $\lp_t$ is conditionally Poisson given $\mathcal{F}^{\eta}_t$
    in the sense of \eqref{eqn:conditionally_poisson}.
\end{proposition}

\begin{proof}[of Proposition~\ref{thm:mmt_application}]
    This is the content of the Markov Mapping Theorem applied to our situation,
    \citet[Thm A.2 in][]{etheridge/kurtz:2018}.
    In the notation of that theorem, $\gamma$ is as above,
    $\alpha$ is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
    or as a Poisson process with Lesbegue intensity (in the limiting case),
    and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
    for all $f \in \mathcal{D}(A^N)$ (and similarly a function $\psi$ for $A$).
    We also need that applying the lookdown generator to a function and averaging over levels
    is equivalent to applying the population process generator to the function
    whose dependence on levels has been averaged out,
    which we precisely state, and verify, in Appendix~\ref{sec: Markov Mapping Theorem Application}.

    For finite $N$,
    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
    we can use $\psi^N(\lp) = \langle C + u |F(x, \eta)|, \lp(dx, du) \rangle$
    for an appropriate constant $C$.
    For the scaling limit, recall that the test functions $f$ are of the form
    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
    with $g(x, u) = 1$ for $u \ge u_0$,
    and so taking for example the mostly troublesome term in $Af(\lp)$,
    we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
    \begin{align*}
        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
        & \le
        \| \partial_u g \|_\infty \sum_{(x, u) \in lp} | F(x, \eta) u \ind_{u \le u_0} | \\
        & \le
        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in lp} | F(x, \eta) u e^{-u} | .
    \end{align*}
    The second line would be just what we want,
    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
    So, the third line provides us with the required bound,
    absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
    and $\langle |F(x, \eta u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
    To do this we must restrict $\lp$ to lie in the space of measures
    for which this is finite.
\end{proof}

@@

\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
    As in Section~\ref{sec:population_density_proof},
    the theorem will follow from tightness and characterization of the limit.
    This time, the processes $\lp^N$ take values in $\lpmeasures$,
    the space of locally finite measures on space $\times$ levels.
    (They will in fact be point measures, including the limit,
    but that is a consequence of this theorem.)
    Again, tightness follows from a compact containment condition,
    tightness of one-dimensional distributions,
    and an application of \citet{EK} Theorem~3.9.1.

    Lines of descent can escape to infinite level in finite time, and so
    we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
    induced by test functions on $\overline{\IR^d} \times [0,\infty)$
    of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
    and $h \in C_c([0, \infty))$.
    This space is completely metrizable,
    and we may choose a countable set of nonnegative, compactly supported $f_k$
    such that a subset $K \subset \lpmeasures$ is relatively compact if and only if
    $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
    therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.

@@

What we need for compact containment will come from the following Lemma.
The generality is unimportant --
for concreteness one may take $h(u) = e^{-u}$.

\begin{lemma}
        \label{lem:h_containment}
    Let $h$ be a positive, continuous, nondecreasing, differentiable function on $[0, \infty)$
    such that
    $\int_0^\infty \int_u^\infty h(v) dv du$,
    $\int_0^\infty u^2 |h'(u)| du$,
    and $\int_0^\infty h(u)^2 du$
    are all finite,
    Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$ there exists a constant $K$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M \right\}
    <
    \frac{K}{M} .
    $$
\end{lemma}

We postpone the proof of this Lemma to show how it gets us to compact containment.
First, we show that this implies compact containment for arbitrary
compactly supported functions.

\begin{lemma}
    \label{lem:compact containment hn}
    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
    for any $T$ and $k$ there exists a constant $K_k$ such that for all $M > 0$,
    $$ 
    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
    <
    \frac{K_k}{M} .
    $$
\end{lemma}

\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
    Let $h$ be as in Lemma~\ref{lem:h_containment}.
    For any $f \in C(\bar \IR^d \times [0, \infty))$ with compact support,
    there is a $c_f < \infty$ such that $f(x, u) \le c_f h(u)$.
    Therefore, $\langle f, \xi \rangle \le \langle h, \xi \rangle$,
    and so by Lemma~\ref{lem:h_containment},
    \begin{align*}
        \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle f, \lp^N_t \rangle > M \right\}
        \le
        \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M/c_f \right\}
        <
        \frac{K c_f}{M} .
    \end{align*}
\end{proof}

@@

In other words, the processes $\lp^N$ stay in 
the compact set
$$
    \left\{
        \lp \in \lpmeasures \;:\;
        \langle h_k, \lp \rangle \le C_k
        \text{ for all } k \ge 1
    \right\} ,
$$
for all $0 \le t \le T$
with uniformly high probability.
\comment{
    Note that we could instead of the vague topology on locally finite measures,
    take the space of measures with $\langle h, \xi \rangle < \infty$
    for which $\xi_n \to \xi$ if $\langle f, \xi \rangle < \infty$ for all $f$ for which $f \le c_f h$,
    which is completely metrizable
    as in Condition 2.1 of \citet{etheridge/kurtz:2019}.
}

@@

Finally, we prove the key lemma.

\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
    \comment{(TODO: shorten and make constants have reasonable notation)}
    Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
    \begin{align*}
    \begin{split}
        \langle h, \lp_t^N \rangle
        &=
        \langle h, \lp_0^N \rangle
        + M^{h}_t 
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 c^N(x, \eta^N_s) \int_u^N h(v) dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds
        \\ & \qquad \qquad {}
        +
        \int_0^t
        \big\langle
            \left(
                c^N(x, \eta^N_s) u^2
                - b^N(x, \eta^N_s) u
            \right)
            h'(u)
        ,
        \lp_s^N(dx, du) \big \rangle
        ds ,
    \end{split}
    \end{align*}
    where $M^{h}_t$ is a martingale
    with quadratic variation
    \begin{align*}
        [M^{h}]_t
        &=
        \int_0^t
        \langle 2 c^N(x, \eta_s^N) \int_u^N h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{align*}
    Now, note that $0 \le c^N(x, \eta_x^N) \le C_a < \infty$
    and $b^N(x, \eta_s^N) \le C_b < \infty$,
    and we have assumed that $h'(u) \le 0$ (since $h$ is nonincreasing),
    so we may bound
    \begin{align} \label{eqn:hn_bound},
    \begin{split} 
        \langle h, \lp_t^N \rangle
        &\le
        \langle h, \lp_0^N \rangle
        + M^{h}_t
        \\ & \qquad {}
        +
        \int_0^t
        \big\langle
            2 C_a \int_u^\infty h(v) dv
            + \left( C_a u^2 + C_b u \right) |h'(u)|
        ,
        \lp_s^N(dx, du) \big \rangle
        ds .
    \end{split}
    \end{align}
    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
    we know that for appropriate $f$,
    $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
    where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
    By our assumptions on $h$,
    we know that
    $$
        \int_0^\infty \left( 2 C_a \int_u^\infty h(v) dv
        + \left( C_a u^2 + C_b u \right) |h'(u)| \right) du
        < C
    $$
    for some $C < \infty$, and so
    \begin{align*}
    \begin{split}
        \IE\left[ \langle h, \lp_t^N \rangle \right]
        &\le
        \IE\left[ \langle h, \lp_0^N \rangle \right]
        +
        C
        \int_0^t
        \IE\bigg[
            \big\langle
            1
            ,
            \eta_s^N(dx, du) \big \rangle
        \bigg]
        ds ,
    \end{split}
    \end{align*}
    which we know by Lemma~\ref{lem:eta_f_bound}
    is bounded by $C_0 e^{C_1 t}$ for some other constants $C_0$ and $C_1$.

@@

    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
    The Burkholder-Davis-Gundy inequality
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c^N(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & =
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C'' e^{C_1 T} ,
    \end{align*}
    for a constant $C''$ which is finite
    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.

@@

\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
    Again, we use the Aldous-Rebolledo criterion.
    Tightness of $\langle f, \lp_t \rangle$ for a fixed $t$
    follows from Lemma~\ref{lem:compact containment hn},
    so we need only prove conditions analogous to
    \eqref{eqn:eta_projections_goal1}
    and \eqref{eqn:eta_projections_goal2}
    applied to the martingale representation
    of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
    Indeed, the proof follows exactly as the proof of
    Lemma~\ref{lem:eta_projections_tightness},
    except that terms are bounded by constant multiples of $\langle h, \xi^N_s \rangle$
    instead of $\langle 1, \eta^N_s \rangle$.
    There is only one term that might use explanation,
    which is
    \begin{align*}
        &
        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
        \\ &\qquad
        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
    \end{align*}
    but this is now bounded as in the proof of Lemma~\ref{lem:eta_f_bound}.
\end{proof}

@@
